Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
Rework configuration overview section

\noindent {\bfseries Overview}
There is a configuration interface (Figure ~\ref{fig:interface}) to help guide users through 
setting up their connection to the Tor network. Through this, users can configure Tor to set up a bridge,
proxy, or both. Since proxies are not a Tor-specific notion nor explicitly required to circumvent censorship, 
we will focus our study on bridge configuration. We accomplish this by placing users in crafted simulated 
censorship environments which require particular bridge configurations to circumvent censorship.

Our hypothesis is that the average user does not have knowledge
knowledge on how certain pluggable transports work, or to provide non-publicly listed IP
addresses bridges. Certain real-world censorship settings require the user to provide this
information during configuration, which will affect how successful users are at 
circumventing censorship using Tor. Participants may receive additional information through word 
of mouth, help from relatives, or blogs. Our study will measure if the configuration
interface successfully guides users to correctly configuring their browser, not accounting 
for any additional  information that a real user may have.\\

>>>>

\noindent {\bfseries Overview}
The Tor Browser provides a configuration interface (Figure
~\ref{fig:interface}) to guide users through setting up their connection to the
Tor network. While people in most countries can connect to Tor using the
dialog's default settings, citizens in certain censorship environments must
make use of additional settings, such as bridges, proxies, or both.

Our hypothesis is that, under these circumstances, the average user will
struggle to connect, because they lack knowledge of the technical terms and
mechanisms required for circumvention (such as pluggable transports) and cannot
obtain information not explicitly provided by the user interface (e.g., IP
addresses of non-publicly listed bridges).

Our study will test this hypotheses by measuring if the connection
interface successfully guides users to correctly configuring their browser.\\
